---
title: "P8105 Homework 1 (zw2975)"
output: github_document
---

```{r library, include = FALSE}
# load library
library(palmerpenguins)
```

## Problem 1

```{r get data from package}
# load the dataset from package
data("penguins", package = "palmerpenguins")
```
#### short descirption of the penguins dataset:
The `Penguins` dataset has variables `species`, `island`, `bill_length_mm`, `bill_depth_mm`, `body_mass_g`, `sex`, and `year`.
This dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean flipper length of this dataset is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.

#### Scatter plot for bill length vs. flipper length
```{r load library ggplot2, include = FALSE}
library(ggplot2) #for graphing scatterplot
```

```{r making scatterplot, warning = FALSE}
# saving the plot with a name
bill_flipper <- ggplot(penguins, aes(x = bill_length_mm , y = flipper_length_mm, color = species)) +
  geom_point() + 
  labs(title = "Bill length vs. flipper length for different species", 
       x = "Bill length in mm",
       y = "Flipper length in mm")

print(bill_flipper) #display the scatterplot

ggsave("bill_flipper.png") #saving plot in project
```
## Problem 2
```{r load tydiverse, include = FALSE}
library(tidyverse)
```

```{r create dataframe}
dataframe <- tibble(
  x = rnorm(10), # it has a size 10 with standard normal distribution
  vec_logical = x > 10, # True if x>10, false if x is not >10
  vec_char = c("Hello", "my", "name", "is", "Zhiyu","Wei", "nice", "to", "meet", "you"), # 10 characters
  vec_factor = c("1", "2", "3","1", "2", "3", "1", "2", "3", "3" )) # 3 factor levels assigned to each character
```


```{r take mean, warning = FALSE}
# try to take mean for each variable
# mean of the numeric variable
mean(dataframe 
     %>% pull(x))
# mean = 0.09992325

# mean of the logical variable
mean(dataframe 
     %>% pull(vec_logical))
# mean = 0

# mean of the character variable
mean(dataframe 
     %>% pull(vec_char))
# mean is NA

# mean of the factor variable
mean(dataframe 
     %>% pull(vec_factor))
# mean is NA
```


```{r change to numeric, echo = TRUE, results='hide', warning = FALSE}
# logical variable to numeric
as.numeric(dataframe$vec_logical)

# character variable to numeric
as.numeric(dataframe$vec_char)

# factor variable to numeric
as.numeric(dataframe$vec_factor)
```
#### What happened?
I got a warning saying that NAs are created due to coercion. 
The logical variable all became 0.
The character variable all became NA.
The factor variable has numeric values now but that is because the levels were originally set to be numbers. 

